FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-12-07 NewVersion/sections/Auxiliary.tex
uncommitted stuff

We present the type soundness of the model by a few theorems below, following the standard technique of
subject reduction and progress proposed by Wright and Felleisen~\cite{Wright1994}. The proof, together with some lemmas, are
in Appendix. Type soundness states that if an expression is well-typed, then after many reduction
steps it must reduce to a value, and its annotation is the same as the static type of the original expression.

@@

Our theorems are stricter than those of Featherweight Java~\cite{Igarashi01FJ}. Specifically, in both term substitution (a lemma in Appendix)
and subject reduction, reduction may lead to a term with a subtype in
FJ, but in \MIM{} types are unchanged. The difference is due to
%%subtyping; the parameter or \lstinline|this| reference requires some type $I$, but a value with a more specific type,
%%which is subtype of $I$, can be passed. However, as 
the fact that \MIM{} keeps track of the static types during
reduction. 
In FJ, the information about the static types is lost.

>>>>

We present the type soundness of the model by a few theorems below, following the standard technique of
subject reduction and progress proposed by Wright and Felleisen~\cite{Wright1994}. The proof, together with some lemmas, is presented 
in Appendix. Type soundness states that if an expression is well-typed, then after many reduction
steps it must reduce to a value, and its annotation is the same as the static type of the original expression.

@@

Our theorems are stricter than those of Featherweight Java~\cite{Igarashi01FJ}. In FJ, the subject reduction theorem states that 
after a step of reduction, the type of an expression may change to a subtype due to subtyping. However, in \MIM{}, 
the type remains unchanged because we keep track of the static types and use them for casting during
reduction.
